EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
Edits

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 5th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2017, four tools competed on a set of open source Java
classes. This paper describes the results of applying the \EVOSUITE
test generation tool~\cite{FrA11c} in this competition. Details about
the procedure of the competition, the technical framework, and the
benchmark classes can be found in~\cite{sbst17competition}.  In this
competition, \EVOSUITE achieved a 1457.3 overall score, which was the
highest among the competing and baseline tools.

@@

The configuration of \EVOSUITE for the competition is largely based on
its default values, since these have been tuned
extensively~\cite{arcuri2013parameter}. We used the default set of
coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
branch coverage, branch coverage by direct method invocation, weak
mutation testing, output coverage, exception coverage). The use of an
archive of solutions~\cite{emse_archive}, which iteratively removes
covered goals from the fitness function and stores the corresponding
test cases is now enabled by default in \EVOSUITE.

@@

% Look at benchmarks that always failed
\EVOSUITE failed to produce any test suite for benchmarks JXPATH-7 and
OKHTTP-8, and also struggled often for benchmarks LA4J-3, LA4J-7,
BCEL-9 (highlighted in Table~\ref{table:results}). All executions of
\EVOSUITE for JXPATH-7 failed in the instrumentation phase as a result
of exceeding Java's 64k limit on the size of methods. A viable fix
would be to stop instrumenting before the limit is reached, at the
price of limited search guidance; a more effective solution would
involve identifying parts of the code that are worth instrumenting. A
missing dependency for OKHTTP-8 caused all executions---\emph{for all
  tools}---to fail. For the other mentioned benchmarks, the failure
reasons (in some cases related to sandboxing, mocking and timeouts)
will require further investigation.

% Look at benchmarks where coverage decreased with increased budget
As expected, both branch coverage and mutation score generally
increased with higher time budgets, although in some cases, specially
with $budget=300s$, a decrease was observed for some
benchmarks. Having run only three repetitions of the tool per time
budget, it is fair to assume the decreases are due to bugs affecting
executions by chance. A preliminary investigation on the source of
this loss of coverage revealed that memory management (e.g.,
out-of-memory errors for OKHTTP-2 and RE2J-7), sandboxing (e.g.,
affecting all executions for LA4J-3 and LA4J-7), and mocking
(affecting BCEL-1, BCEL-5 and BCEL-7, for example) are some of the
aspects that require attention and debugging in \EVOSUITE.

@@

% Look at benchmarks with more flaky tests
Flaky tests continue to be a challenge for test generation. Benchmarks
FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
tests in one run (12 and 14, respectively). In both cases, the
minimisation phase timed out and hence \EVOSUITE reverted the
resulting test suite to the previous, unminimised one, which as
mentioned before, is more likely to break. Techniques such as
\textit{partial minimisation} to only select a few test cases to be
minimised, rather than all test cases; or
\textit{delta-debugging}~\cite{zellerdd}, which could isolate the
relevant statements of each test case, might be worth investigating
to alleviate this issue.

>>>>

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 5th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2017, four tools competed on a set of open source Java
classes. This paper describes the results of applying the \EVOSUITE
test generation tool~\cite{FrA11c} in this competition. Details about
the procedure of the competition, the technical framework, and the
benchmark classes can be found in~\cite{sbst17competition}.  In this
competition, \EVOSUITE achieved an overall score of 1457.3, which was
the highest among the competing and baseline tools.

@@

The configuration of \EVOSUITE for the competition is largely based on
its default values, since these have been tuned
extensively~\cite{arcuri2013parameter}. We used the default set of
coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
branch coverage, branch coverage by direct method invocation, weak
mutation testing, output coverage, exception coverage). The use of an
archive of solutions~\cite{emse_archive}, which iteratively removes
covered goals from the fitness function and stores the corresponding
test cases, is now enabled by default in \EVOSUITE.

@@

% Look at benchmarks that always failed
\EVOSUITE failed to produce any test suites for benchmarks JXPATH-7 and
OKHTTP-8, and also struggled often for benchmarks LA4J-3, LA4J-7,
BCEL-9 (highlighted in Table~\ref{table:results}). All executions of
\EVOSUITE for JXPATH-7 failed in the instrumentation phase, where
Java's 64k limit on the size of methods was exceeded. A viable fix
would be to stop instrumenting before the limit is reached, at the
price of limited search guidance; a more effective solution would
involve identifying parts of the code that are worth instrumenting. A
missing dependency for OKHTTP-8 caused all executions---\emph{for all
  tools}---to fail. For the other mentioned benchmarks, the failure
reasons (in some cases related to sandboxing, mocking and timeouts)
will require further investigation.

% Look at benchmarks where coverage decreased with increased budget
As expected, both branch coverage and mutation score generally
increased with higher time budgets, although in some cases, especially
with $budget=300s$, a decrease was observed for some
benchmarks. Having run only three repetitions of the tool per time
budget, it is fair to assume the decreases are due to bugs affecting
executions by chance. A preliminary investigation on the source of
this loss of coverage revealed that memory management (e.g.,
out-of-memory errors for OKHTTP-2 and RE2J-7), sandboxing (e.g.,
affecting all executions for LA4J-3 and LA4J-7), and mocking
(affecting BCEL-1, BCEL-5 and BCEL-7, for example) are some of the
aspects that require attention and debugging in \EVOSUITE.

@@

% Look at benchmarks with more flaky tests
Flaky tests continue to be a challenge for test generation. Benchmarks
FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
tests in one run (12 and 14, respectively). In both cases, the
minimisation phase timed out and hence \EVOSUITE reverted the
resulting test suite to the previous, unminimised one, which as
mentioned before, is more likely to break. Techniques such as
\textit{partial minimisation} to only select a few test cases to be
minimised, rather than all test cases, or
\textit{delta-debugging}~\cite{zellerdd}, which could isolate the
relevant statements of each test case, might be worth investigating
to alleviate this issue.
